---
title: "R Objects, Workflow, and Functions"
format: html
editor: visual
---
# Vectors

Create a vector
```{r}
set.seed(14)
my_unit <- runif(30)
is.vector(my_unit)
```


Subset that object
```{r}
my_unit[1:10]
my_unit[c(1:3, 15:17)]
```

Sort the vector
```{r}
sort(my_unit)
```

Create a vector with strings in it
```{r}
char_vec <- c('daf', "adf", "e2", '15dsa')
sort(char_vec)
```

# Data Frames

```{r}
data(trees)
trees
str(trees)
```
Subset a column
```{r}
trees$Height
```

Get attributes from the dataframe
```{r}
attributes(trees)
names(trees)
colnames(trees) [2:3]
```

# Lists

Investigating data frame from before
```{r}
is.list(trees)
is.data.frame(trees)
```
Can subset as a list
```{r}
trees[1]
trees[[1]]
```

Look at linear model fit 
```{r}
fit <- lm(Volume ~ Height + Girth, data = trees)
fit
```
Look at structure but restrict info:
```{r}
str(fit, max.level = 1)

```

Some helper functions exist... helper functions are to grab a particular attribute.
```{r}
fit$coefficients
coef(fit)
fit$residuals
```

# If/Then/Else

Logical Statements for Subsetting Data
```{r}
head(iris)
iris$Species == 'setosa'
iris[iris$Species == 'setosa',]
```

Example of if/then/else
```{r}
head(airquality)
airquality$Wind
```
```{r}
if(airquality$Wind[1] >= 15) {
  "High Wind"
} else if(airquality$Wind[1] >= 10) {
  "Windy"
} else if(airquality$Wind[1] >= 6) {
  "Light Wind"
} else if(airquality$Wind[1] >= 0) {
  "Calm"
} else {
  "Error"
}
```
Fizz Buzz Challenge
- Take in a number
  if it is divisible by 3 return fizz
  if it is divisible by 5 return buzz
  if it is divisible by 15 return fizz buzz
```{r}
number <- 2
if((number %% 15) == 0) {
  print("fizz buzz")
} else if((number %% 5) == 0) {
  print("buzz")
} else if((number %% 3) == 0) {
  print("fizz")
} else {
  print("Whoops?")
}
#if(!number %% 15)
```
  

# Loops

